---
title: "The Effects of Primary Care Clinic Closures: How Older People's Geographical Distance to Care Affects Their Health and Service Use?"
author: --
format: gfm
editor: visual
---

# The effects of primary care clinic closures: How older people's geographical distance to care affects their health and service use?

## Setup

```{r}
#| label: preliminaries
#| echo: true
#| output: false
#| message: false
#| warning: false

# Load 'here' package for relative file paths
  library(here)

# Run setup script
  source(here::here("scripts", "setup.R"), echo = FALSE)
```

## Identifying closed stations

Running data to identify health station closures and new station entries

```{r}
#| label: coordinates
#| echo: true
#| message: false
#| warning: false
#| output: false
#| results: false

# Run script
  source(here::here("scripts", "identifying_closed_stations.R"), echo = FALSE)

```

## Maps

Drawing map of closed clinics with population density:

```{r}
#| label: map
#| echo: true
#| message: false
#| warning: false
#| output: true
#| results: false
#| fig-width: 6
#| fig-height: 8
#| fig-align: center


# Running script to draw the maps
  source(here::here("scripts", "map_closures.R"), echo = FALSE)

```

Drawing map with all stations: all closed stations marked with yellow squares. All new clinics marked with purple squares.

```{r}
#| label: map2
#| echo: true
#| message: false
#| warning: false
#| output: true
#| results: false
#| fig-width: 6
#| fig-height: 8
#| fig-align: center


# Running script to draw the maps
  source(here::here("scripts", "map_all_clinics.R"), echo = FALSE)
```

## Municipality level descriptive statistics

Descriptive statistics at municipality level. Treatment (\>1 closure in municipality) and control (no closures) group mean, standard deviation, and relative difference.

Source: Thl (<https://sotkanet.fi/sotkanet/fi/index>)

```{r}
#| label: map2
#| echo: true
#| message: false
#| warning: false
#| output: true
#| results: false

# Running script to make table
  source(here::here("scripts", "mun_level_summary_table.R"), echo = FALSE)
```
