---
title: "The Effects of Primary Care Clinic Closures: How Older People's Geographical Distance to Care Affects Their Health and Service Use?"
author: --
format: gfm
editor: visual
---

# The effects of primary care clinic closures: How older people's geographical distance to care affects their health and service use?

## Setup

```{r}
#| label: preliminaries
#| echo: true
#| output: false
#| message: false
#| warning: false

# Load 'here' package for relative file paths
  library(here)

# Run setup script
  source(here::here("scripts", "setup.R"), echo = FALSE)
```

## Identifying closed stations

Running data to identify health station closures and new station entries. The data is collected from public sources using Internet Archive WayBack Machine (DOI will be added).

```{r}
#| label: coordinates
#| echo: true
#| message: false
#| warning: false
#| output: false
#| results: false

# Run script
  source(here::here("scripts", "identifying_closed_stations.R"), echo = FALSE)

```

## Maps

Drawing a map of closed clinics with population density.

Closed health stations are marked with red squares. Population density is calculated by dividing the population of the postal code area by the area of the postal code region (km2). To improve map readability, population density values are truncated at 100 people per square kilometre---all areas exceeding this threshold are capped at 100, regardless of their actual density.

```{r}
#| label: map
#| echo: true
#| message: false
#| warning: false
#| output: true
#| results: false
#| fig-width: 6
#| fig-height: 8
#| fig-align: center


# Running script to draw the maps
  source(here::here("scripts", "map_closures.R"), echo = FALSE)

```

Drawing map of stations closed and opened during the study period relative to other stations that did not close.

All closed stations are marked with yellow squares, new clinics marked with purple squares, and others that remain (mostly) in the same location are marked with green squares.

```{r}
#| label: map2
#| echo: true
#| message: false
#| warning: false
#| output: true
#| results: false
#| fig-width: 6
#| fig-height: 8
#| fig-align: center


# Running script to draw the maps
  source(here::here("scripts", "map_all_stations.R"), echo = FALSE)
```

## Municipality level descriptive statistics

Descriptive statistics at municipality level. Treatment (\>1 closure in municipality) and control (no closures) group mean, standard deviation, and relative difference.

Source: THL (<https://sotkanet.fi/sotkanet/fi/index>)

```{r}
#| label: summary_table
#| echo: true
#| message: false
#| warning: false
#| output: true
#| results: false

# Running script to make table
  source(here::here("scripts", "mun_level_summary_table.R"), echo = FALSE)

```

## Finnish healthcare system chart: patient pathways

The system chart visualizing the patient pathways, structure and distribution of visits among the elderly population. Primary care is provided independently by nurses, GPs, and specialists. Specialised care is typically provided by specialists assisted by nurses. Shares of the service use of different subsystems among people aged over 64 years are from THL Sampo -datacubes ([Sampo](https://sampo.thl.fi/pivot/prod/fi/hilmokokonaisuus/kuutio01/fact_hilmokok_kuutio01?row=palvelu-49937&row=palvelusektori-918725&column=ikaluokka-109987&filter=measure-87578&filter=aika-660839)).

```{r}
#| label: system_graph
#| echo: true
#| message: false
#| warning: false
#| output: true
#| results: true

source(here::here("scripts", "system_chart.R"), echo = FALSE)

```
